Non-Vertical Cultural Transmission and the\\ Evolution of Cooperation

### 2020-08-22 ms/main.tex
fix figure 4

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[htb]
\centering
\includegraphics{coexistence_without_oblique.pdf}
\caption{\textbf{Stable and unstable coexistence between cooperation and defection - with oblique transmission.} The frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ is plotted as a function of the frequency in the current generation $\tilde{p}$.
The line $\tilde{p}'=\tilde{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\tilde{p}^*$ (black circle).
When the curves are above the dashed line ($\tilde{p}<\tilde{p}^*$) the frequency $\tilde{p}$increases towards $\tilde{p}^*$.
When the curves are below the dashed line ($\tilde{p}>\tilde{p}^*$) the frequency $\tilde{p}$ decreases towards $\tilde{p}^*$.
The yellow curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $\alpha = 0.45$. For those values we get that $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients})
The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$. For those values we can that $\beta_3<\beta_1$}
\label{fig:coexistence_without_oblique}
\end{figure}

@@

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[htb]
  \centering
  \includegraphics{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable and unstable coexistence between cooperation and defection - without oblique transmission.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted as a function of the frequency in the current generation $\hat{p}$.
  The line $\hat{p}'=\hat{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle).
  When the curves are above the dashed line ($\hat{p}<\hat{p}^*$) the frequency $\hat{p}$increases towards $\hat{p}^*$.
  When the curves are below the dashed line ($\hat{p}>\hat{p}^*$) the frequency $\hat{p}$ decreases towards $\hat{p}^*$.
  The yellow curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$. For those values we get that $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
  The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$. For those values we can that $\gamma_1<c<\gamma_2$}
  \label{fig:coexistence_with_oblique}
  \end{figure}

>>>>

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[htb]
\centering
\includegraphics{coexistence_without_oblique.pdf}
\caption{\textbf{Stable and unstable coexistence between cooperation and defection - without oblique transmission.} The frequency of the cooperative phenotype $A$ among parents in the next generation $\tilde{p}'$ is plotted as a function of the frequency in the current generation $\tilde{p}$.
The line $\tilde{p}'=\tilde{p}$ is shown as a dashed black line. The curves and dashed line intersect at the equilibrium $\tilde{p}^*$ (black circle).
When the curves are above the dashed line ($\tilde{p}<\tilde{p}^*$) the frequency $\tilde{p}$increases towards $\tilde{p}^*$.
When the curves are below the dashed line ($\tilde{p}>\tilde{p}^*$) the frequency $\tilde{p}$ decreases towards $\tilde{p}^*$.
The yellow curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 12$, $c=0.35$, $\alpha = 0.45$. For those values we get that $\gamma_2<c<\gamma_1$ (\autoref{eq:cost_boundaries})
The blue curve is \textbf{unstable coexistence} and has the following parameters values: $T_A = 0.5$, $T_B = 0.1$, $b = 1.3$, $c=0.904$, $\alpha = 0.4$. For those values we can that $\gamma_1<c<\gamma_2$}
\label{fig:coexistence_without_oblique}
\end{figure}

@@

%%% Figure: coexistence map - without oblique transmission
\begin{figure}[htb]
  \centering
  \includegraphics{coexistence_with_oblique.pdf}
  \caption{\textbf{Stable coexistence between cooperation and defection - with oblique transmission.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted as a function of the frequency in the current generation $\hat{p}$.
  The line $\hat{p}'=\hat{p}$ is shown as a dashed black line. The curve and dashed line intersect at the equilibrium $\hat{p}^*$ (black circle).
  When the curves are above the dashed line ($\hat{p}<\hat{p}^*$) the frequency $\hat{p}$increases towards $\hat{p}^*$.
  When the curves are below the dashed line ($\hat{p}>\hat{p}^*$) the frequency $\hat{p}$ decreases towards $\hat{p}^*$.
  The curve is \textbf{stable coexistence} and has the following parameters values:  $T_A = 0.4$, $T_B = 0.9$, $b = 20$, $c=0.1$, $\alpha = 1$, $v=0.4$. For those values we get that $0<\beta_3<\beta_1$ (\autoref{eq:polynomial_coefficients})}
  \label{fig:coexistence_with_oblique}
  \end{figure}
